Bibliometrics

### 2024-11-11 data-raw/01-bibliometrics-analysis.qmd
Pushing latest changes to bibliometric analysis

library(bibliometrix) # Comprehensive Science Mapping Analysis
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(ggraph) # An Implementation of Grammar of Graphics for Graphs and Networks
library(glue) # Interpreted String Literals
library(here) # A Simpler Way to Find Your Files
```

@@

>>>>

library(bibliometrix) # Comprehensive Science Mapping Analysis
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(ggraph) # An Implementation of Grammar of Graphics for Graphs and Networks
library(glue) # Interpreted String Literals
library(here) # A Simpler Way to Find Your Files
library(tidytext)
```

@@

Who are the authors in that niche that cites both Wilson and Hansen, and what is the temporal pattern of publication?
```{r}
corpus |> 
  filter(corpus == "Both") |> 
  select(AU, PY) |> arrange(PY)
```

<!--
```{r}
CS <- conceptualStructure(corpus,
                          field="DE",
                          method="MCA",
                          minDegree=4, 
                          clust=5, 
                          stemming = TRUE,
                          labelsize = 10,
                          documents = 10)
```

-->

```{r}
corpus |> tibble::rownames_to_column(var = "rownames") |> select(rownames, AB) |> unnest_tokens(word, input = "AB")
```
